Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
another pass

Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
relative to \sfl{}$^{k}$. The figure shows a histogram over
$\Delta{}C$ for different values of $k$. Note that (1) the number of
cases where the baseline outperforms \combpar{k} is small (\eg{}, $33$
of the \numFaults\ faults for $k=10$) and that (2) the number of cases
\combpar{k} outperforms the baseline is significative (\eg{}, $117$ of
the \numFaults\ faults for $k=10$). One of the following reasons
justifies the baseline outperforming \combpar{k}:\Mar{following
  sentence is confusing IMO. suggest to clarify or remove. aren't
  points two and three equivalent? as for one, isn't foo an issue both
  for \combpar{k} and \sfl{}$^{k}$?} (1) a fault of omission, (2) the
test has design limitations which \ds~is not capable of handling, or
(3) the buggy-class in not in the top $k$ of the highest-ranked faulty
classes under analysis.

@@

Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$. On
the left-hand-side, the figure shows the distributions of $\Delta{}C$
for different values of $k$, considering all faults except those where
test engineering problems and faults of omission are manifested ($227$
faults). The two negative outliers present the cases where the
buggy-class was not in the top $k$. On the right, we only consider the
cases where at least one of the variants resulted in an increase of
$\Delta{}C$ ($116$ faults), i.e., the cases where \ds{} improves
\sfl. Although, we observe a considerable amount of cases where
$\Delta{}C$ is negative or zero in Figure~\ref{fig:diagnosis}, we also
see that there is a considerable amount of faults which could benefit
a lot with \combpar{k}, in Figure~\ref{fig:boxplot}.

@@

In the following, we present statistical analysis to demonstrate that
the distributions of $C$ for each technique are different.
Table~\ref{table:st}, reports the average rank of all faulty
statements of the \dfj{} faults considered to the study after applying both
techniques, \sfl{}$^{k}$ and \combpar{k} for $k=5$ and $k=10$.
In bold, we present the results of the $227$ faults that do not comprise the
cases that are result of the limitations mentioned before (test design and fault
of omission). These results show that \ds{} improves \sfl{} in a mean
of $6$ ($3.3\%$ on average) statements on the average ranking of all faulty statements,
when considering $k=10$. Inside parentheses, we present the
rank results for all faults which do not report promissing results. However,
if we only consider the faults which can benefit from our approach, 
we can observe that there is a considerable
amount of cases where the approach is actually successful. For
$k=5$, our approach achieves a mean improvement of $41.1$ ($9.57\%$ 
on average) statements on the ranking and an impressive maximum ranking improvement
of $3171$ ($96.7\%$ on average) statements. Whereas for $k=10$, \combpar{k}
achieves a mean improvement of $19$ ($13.35\%$ on average) statements
on the ranking and a maximum ranking improvement
of $209$ ($73.7\%$ on average) statements. Such difference is justified by the fact that
entire files are discarded in \combpar{5}, whose statements are
included in the ranking of \combpar{10}. Consequently, the
improvements obtained by the technique will not be as high if slicing
on these additional files is unable to aggressively and safely discard
statements. This also shows that slicing files, in addition to slicing
statements from those files, is very beneficial for fault localization
performance.

>>>>

%% k=10
\newcommand{\numOutPerformed}{$33$}%
\newcommand{\numEquallyPerformed}{$110$}%

Figure \ref{fig:diagnosis} summarizes performance of \combpar{k}
relative to \sfl{}$^{k}$. The figure shows a histogram over
$\Delta{}C$ for different values of $k$. Note that (1) the number of
cases where the baseline outperforms \combpar{k} is small (\eg{},
\numOutPerformed\ of the \numFaults\ faults for $k=10$) and that (2)
the number of cases \combpar{k} outperforms the baseline is
significative (\eg{}, $117$ of the \numFaults\ faults for $k=10$). One
of the following reasons justifies the baseline outperforming
\combpar{k}:\Mar{following sentence is confusing IMO. suggest to
  clarify or remove. aren't points two and three equivalent? as for
  one, isn't foo an issue both for \combpar{k} and \sfl{}$^{k}$?} (1)
a fault of omission, (2) the test has design limitations which \ds~is
not capable of handling, or (3) the buggy-class in not in the top $k$
of the highest-ranked faulty classes under analysis.

@@

Figure~\ref{fig:boxplot} shows the distributions of $\Delta{}C$ for
different sets of faults as to better understand the performance of
\combpar{k}. On the left-hand-side, we show distributions of
$\Delta{}C$, for different values of $k$, considering all cases where
the predicate $\Delta{}C\geq{}0$ holds, \ie{}, we excluded the
\numOutPerformed\ cases where \sfl{}$^{k}$ outperformed \combpar{k}
(see Figure~\ref{fig:diagnosis}). The boxplots on the right-hand-side
of the figure considers all the cases where the predicate
$\Delta{}C>0$ holds, \ie{}, it additionally excludes from the dataset
the cases of faults where the techniques perform equally.\Mar{sofia,
  are you sure there are no zeros in this dataset? The min. in this
  distibution (as per the base of the plot) seems to be 0.} To sum,
although we observed a relatively small number cases where $\Delta{}C$
is negative (\numOutPerformed) and a high number of cases $\Delta{}C$
is zero (\numEquallyPerformed), we observed that there is a
considerable amount of cases where the use of \combpar{k} would be
very beneficial.

@@

In the following, we present statistical analysis of the techniques.
Table~\ref{table:st} reports descriptive statistics about the
distributions of $C$ for the techniques under different values of $k$.
In bold, we present the results of the $227$ faults that do not
comprise the cases that are result of the limitations mentioned before
(test design and fault of omission). The number in parentheses are
relative to the dataset including all data faults; note that results
for this dataset are \emph{not} encouraging.

These results show that \ds{}
improves \sfl{} in a mean of $6$ ($3.3\%$ on average) statements on
the average ranking of all faulty statements, when considering
$k=10$. 
However, if we only consider
the faults which can benefit from our approach, we can observe that
there is a considerable amount of cases where the approach is actually
successful. For $k=5$, our approach achieves a mean improvement of
$41.1$ ($9.57\%$ on average) statements on the ranking and an
impressive maximum ranking improvement of $3171$ ($96.7\%$ on average)
statements. Whereas for $k=10$, \combpar{k} achieves a mean
improvement of $19$ ($13.35\%$ on average) statements on the ranking
and a maximum ranking improvement of $209$ ($73.7\%$ on average)
statements. Such difference is justified by the fact that entire files
are discarded in \combpar{5}, whose statements are included in the
ranking of \combpar{10}. Consequently, the improvements obtained by
the technique will not be as high if slicing on these additional files
is unable to aggressively and safely discard statements. This also
shows that slicing files, in addition to slicing statements from those
files, is very beneficial for fault localization performance.
